### 2012-12-21 inst/examples/myers-exploration.Rmd
delta 1.5, r 1.3 K 4.5

```{r Myer-explore}
f <- Myers
p <- c(1, 2, 6) 
K <- p[1] * p[3] / 2 + sqrt( (p[1] * p[3]) ^ 2 - 4 * p[3] ) / 2
allee <- p[1] * p[3] / 2 - sqrt( (p[1] * p[3]) ^ 2 - 4 * p[3] ) / 2 # allee threshold
e_star <- (p[1] * sqrt(p[3]) - 2) / 2 ## Bifurcation point 
```

>>>>

```{r Myer-explore}
f <- Myers
p <- c(1.3, 1.5, 4.5) 
K <- 3.5
allee <- 1
# valid only for p[2] = 2
#K <- p[1] * p[3] / 2 + sqrt( (p[1] * p[3]) ^ 2 - 4 * p[3] ) / 2 #
#allee <- p[1] * p[3] / 2 - sqrt( (p[1] * p[3]) ^ 2 - 4 * p[3] ) / 2 # allee threshold
#e_star <- (p[1] * sqrt(p[3]) - 2) / 2 ## Bifurcation point 
```
